Visually pleasing knot projections

### 2023-01-31 inst/jma_rebuttal_2023_01_30.tex

Many of the important badness functions (e.g. separations of nodes or
of non-crossing curve segments) are based purely on local geometry and
need not know what component of a link they refer to.  Perhaps the
overall length of a knot or of a link-component is not a good metric,
and should be replaced with some other functions of the length of
curve segments between crossings.

Some detailed comments on manuscript R2:

Page 6, line 20:  How many (x,y) pairs are there?

Page 6, Line 36: Why "$\mathbb{R}^{50}$"? - Are there a total of 50
parameters?  What are they?  \textcolor{blue}{\\This was not clear and
  I have rephased.  Old text: ``The optimization typically proceeds
  over $\mathbb{R}^{50}$\ldots"`. New text: ``The optimization
  proceeds over $\mathbb{R}^n$ where $n$ is the number of parameters
  needed to specify the path; typically $n\simeq 50$ for the knots
  presented here".\\ \\}

Page 6, Line 39: ``... the overall bending energy." {\tt ->>} 'minimizing
overall bending energy.'
\textcolor{blue}{\\Fixed\\ \\}

### 2023-01-31 inst/jma_knot.tex
fixes #89

To beautify it we need to specify a function of the path that
quantifies its displeasingness, and then minimize this objective
function using numerical methods.  In the package, minimization is
performed using either Nelder-Mead~\cite{nelder1965} or a Newton-type
method~\cite{dennis1983} (gradient information is not available).  The
optimization typically proceeds over $\mathbb{R}^{50}$ and in the
context of the package, the methods appear to be broadly comparable.

>>>>

To beautify it we need to specify a function of the path that
quantifies its displeasingness, and then minimize this objective
function using numerical methods.  In the package, minimization is
performed using either Nelder-Mead~\cite{nelder1965} or a Newton-type
method~\cite{dennis1983} (gradient information is not available).  The
optimization proceeds over $\mathbb{R}^n$ where $n$ is the number of
parameters needed to specify the path; typically $n\simeq 50$ for the
knots presented here.  In the context of the package, the methods
appear to be broadly comparable.
